%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.2, 1 February 2017) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%%
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font
%% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=7.25cm,marginparsep=0.75cm,top=0.5cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage[none]{hyphenat}
\usepackage[document]{ragged2e}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{AccentGreen}{HTML}{339966}
\definecolor{AcePurple}{HTML}{800080}
\definecolor{DarkerPurple}{HTML}{5b005b}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{SomeBlue}{HTML}{4286f4}
\colorlet{heading}{AcePurple}%Sepia}
\colorlet{accent}{DarkerPurple}%AccentGreen}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Max Meinhold}
\tagline{Seeking Spring 2020 Co-op}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{mxmeinhold@gmail.com}
  \phone{(410) 991-5479}
  %\homepage{www.homepage.com/}
  \github{mxmeinhold}
  %% You MUST add the academicons option to \documentclass, then compile with LuaLaTeX or XeLaTeX, if you want to use \orcid or other academicons commands.
%   \orcid{orcid.org/0000-0000-0000-0000}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\marginpar{\makesidebarheader\input{sidebar.tex}}
    \vspace*{-1\baselineskip}
\makecvheader
\end{fullwidth}
%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\vspace{.65\baselineskip}
\cvsection{Education}
\cvevent{Rochester Institute of Technology}{Computer Science B.S.}{2017 -- 2021}{}

\cvsection{Experience}

\cvevent{Syncurity}{API Integrations Intern}{May 2019 -- August 2019}{Remote}
Automated the enumeration and wrapping of APIs and SDKs via Python.
Integrated various tools into a central platform by developing StackStorm packs.

\divider

\cvevent{Emergent Space Technologies}{Software Intern}{June 2016 -- August 2016}{NASA Goddard Spaceflight Center}
Built a GPS solution in MATLAB from the ground up. Analyzed GPS distortion as a factor of the International Space Station's structure for NASA's Global Ecosystems Dynamics Investigation LIDAR project.

%\cvevent{Asexual Community Census}{Data Analyst}{August 2017 -- Current}{}
%Assist in processing and analysis, survey design, and report creation for the annual Asexual Community Survey.

\divider

\cvevent{Classroom Technology Support}{AV Technician}{January 2019 -- Current}{Rochester Institute of Technology}
Conduct installation, configuration, maintenance, and repair of classroom and auditorium AV systems.
\cvevent{}{AV Responder}{January 2018 -- Current}{Rochester Institute of Technology}
Handle customer support for RIT classroom and auditorium AV systems, including general maintenance and immediate issue resolution.

%\divider

\cvsection{Projects}

\project{External Accounts Connector}{https://github.com/ComputerScienceHouse/eac}
Built a broker in Python using Flask that allows Computer Science House members to associate their LDAP account with various third-party OAuth 2.0 identities and automate related management actions.

\divider

\project{Database Execution and Deletion Administrative Self-Service}{https://github.com/ComputerScienceHouse/DEaDASS}
Created a self-service application to allow users to automatically provision and manage both SQL and NoSQL databases. Provides a RESTful API using Java with Spring Boot.

\divider

\project{Quotefault Slack Bot}{https://github.com/mxmeinhold/csh-quotefault-bot}
Developed a Slack bot for Quotefault, a member quote database for Computer Science House. Allows interacting with the service via its associated REST API and utilizes natural language processing techniques to create new views into the data.

\divider

\project{ThemeSwitcher}{https://github.com/mxmeinhold/CSHThemeSwitcher}
Implemented a solution for storing and applying a global stylesheet preference for each user across various internal microservices. Built using AngularJS and Node.js with Express.

%\divider
%
%\project{Scouting Scheduler}{https://github.com/mxmeinhold/ScoutingScheduler}
%Wrote a small application my robotics team to organize match scouting.
%Written in Java with a Swing GUI.

\clearpage
%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
